Assessing Amazon Turker and automated machine forecasts in the Hybrid Forecasting Competition

### 2018-12-13 slides/index.Rmd
try to fix pdf link

`r icon::fa("file")`: [link to paper (on github under docs/)](https://github.com/andybega/asia-polmeth-2019/blob/master/docs/BegerWard_HFC_AsiaPolmeth2019.pdf)

`r icon::fa("slideshare")`: [slide source](https://github.com/andybega/asia-polmeth-2019/tree/master/slides)
]

>>>>

`r icon::fa("file")`: [link to paper (on github under docs/pdf/)](pdf/BegerWard_HFC_AsiaPolmeth2019.pdf)
]
